---
title: "p8105_hw6_xj2249"
author: "xj2249"
date: "11/14/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	fig.width = 8, 
	fig.height = 6,
	out.width = "90%"
)

theme_set(theme_minimal() +  theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "bottom") + theme(legend.title = element_blank()) )

set.seed(1)
```

# Problem1
## load and clean data
```{r}
bw_df <- 
        read_csv("./data/birthweight.csv") %>% 
        janitor::clean_names() %>% 
        mutate(
                babysex = factor(babysex, labels = c("male","female")),
                frace = factor(frace, labels = c("White","Black","Asian","Puerto Rican","Other")),
                malform = factor(malform, labels = c("absent","present")),
                mrace = factor(mrace, labels = c("White","Black", "Asian", "Puerto Rican"))
                )
```

## Model1: my model!
I'd like to put  sex and the gestational age of the baby, mom's weight gain during pregnancy and pre-pregnancy BMI into my model, and the reason is following: In my opinion, the sex and the gestational age of the baby will definitly influence the birthweight, so include them first. Then, mom's weight gain during pregnancy and pre-pregnancy BMI may also be important, since baby gain all their nutrition from moms.

**Here we go!**

```{r}
bw_lm1 <- 
        bw_df %>% 
        lm(bwt~ babysex + gaweeks + ppbmi + wtgain, data = .) 

bw_df %>% 
        add_predictions(bw_lm1) %>% 
        add_residuals(bw_lm1) %>% 
        ggplot(aes(x = pred, y = resid)) +
        geom_smooth(se = F,size = 0.5) + 
        geom_point() +
        geom_hline(yintercept = 0,col = "red",linetype = "dashed") + 
        labs( x = "Fitted values", y = "Residuals", title = "Residual vs Fitted Plot")
        geom_hline(aes(yintercept = ))
```

## Model2
Fit model2 with length at birth and gestational age as predictors.
```{r}
bw_lm2 <- 
        bw_df %>% 
        lm(bwt~ blength + gaweeks, data = .) 
```

## Model3
Fit model3 with head circumference, length, sex, and all interactions.
```{r}
bw_lm3 <-
        bw_df %>% 
        lm(bwt~ blength*bhead*babysex, data = .) 
```

## cross validation
### generate training and testing datasets
```{r}
cv_df <- 
        crossv_mc(bw_df,100) %>% 
        mutate(train = map(train,as_tibble),
               test = map(test,as_tibble))

```

### let's fit models and assess predition accuracy
```{r}
cross_result <-
        cv_df %>% 
        mutate( lm1 =  map(.x = train,~lm(bwt~ babysex + gaweeks + ppbmi + wtgain, data = .x)),
                lm2 =  map(.x = train,~lm(bwt~ blength + gaweeks, data = .x)),
                lm3 =  map(.x = train,~lm(bwt~ blength*bhead*babysex, data = .x)),
                rmse_lm1 = map2_dbl(.x = lm1, .y = test, ~rmse(.x,.y)),
                rmse_lm2 = map2_dbl(.x = lm2, .y = test, ~rmse(.x,.y)),
                rmse_lm3 = map2_dbl(.x = lm3, .y = test, ~rmse(.x,.y))
                ) %>% 
        select(starts_with("rmse")) %>% 
        pivot_longer(
                everything(),
                names_to = "model",
                values_to = "rmse",
                names_prefix = "rmse_") 

cross_result %>%
        mutate(model = factor(model)) %>% 
        ggplot(aes(x = model, y = rmse,fill = model)) +
        geom_violin() +
        labs( title = "Model comparison by RMSE")
```

It breaks my heart! My model looks worst...with much higher RMSEs than other two models. The third one is the best, with the lowest RMSEs and the second model ranks second.  

# Problem2
```{r load weather data,echo=F}
weather_df <- 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## point estimates 
```{r}
slr = lm(tmax~tmin, data = weather_df)

point_estimates <- tibble(log_b0_b1 =
                                  slr %>% 
                                  broom::tidy() %>% 
                                  pull(estimate) %>% 
                                  prod() %>% 
                                  log() ,
                          r_squared = slr %>% 
                                  broom::glance() %>% 
                                  pull(r.squared) 
                          )

point_estimates %>%  kableExtra::kable(caption = "point estimates")
```

## Boostrap!!!
```{r}
estimates <-
        weather_df %>% 
        bootstrap(100) %>% 
        mutate(slr = map(.x = strap, ~lm(tmax~tmin, data = .x)),
               est1 = map(slr,broom::tidy),
               est2 = map(slr,broom::glance),
               log_b0_b1 = map_dbl(.x = est1, ~.x %>% pull(estimate) %>% prod %>% log ),
               r_squared = map_dbl(.x = est2, ~.x %>% pull(r.squared))
               ) %>% 
        select(.id,log_b0_b1,r_squared)

```

## plot distribution of estimates
```{r}
estimates %>% 
        ggplot(aes(x = log_b0_b1)) +
        geom_density() +
        labs( x = expression("log("~hat(beta)[0]~"*"~hat(beta)[1]~")"),
              title = expression("Distribution of log("~hat(beta)[0]~"*"~hat(beta)[1]~")"))

estimates %>% 
        ggplot(aes(x = r_squared)) +
        geom_density() +
        labs( x = expression(hat(r)^2),
              title = expression("Distribution of"~hat(r)^2))
```

## 95% confidence intervals
```{r}
ci <- 
        estimates %>% 
        pivot_longer(
                -.id,
                names_to = "estimates",
                values_to = "value"
        ) %>% 
        group_by(estimates) %>% 
        summarise( p2.5 = quantile(value,0.025),
                   p97.5 = quantile(value,0.975),
                  se = sd(value)
        ) %>% 
        cbind(., point_estimates = t(point_estimates)) %>% 
        mutate( CI_lower = round(point_estimates -  se * p2.5,digits = 3),
                CI_upper = round(point_estimates +  se * p97.5,digits = 3),
                CI = str_c(CI_lower,CI_upper,sep = ",")) 

ci %>%  kableExtra::kable(caption = "95% confidence interval",digits = 3,align = "c")
```

Therefore, the 95% confidence interval for log_b0_b1 is (`r ci[1,8]`), for r_hat_squared is (`r ci[2,8]`).
